\begin{itemize}
	\item Two sets of sessions from one case study: Application portal case study. 
	\item 1. Full case study
	\item 2. subset of full case study(1244 sessions)
	\item Also do such a nice table pharms uses here
	\item Full Case study: Over 500 users, more than 350000 events. (screenshot of application portal here?)
	\item Format is XML. (show nice xml input here)
	\item When running the full case study alot of perfomance problems came up.
	\item Memory consumption and computation time grew alot due to the nature of the algorithm
	\item Computation moved from a Intel(R) Core(TM) i5-2520M CPU @ 2.50GHz with 8GB Ram to a AMD Opteron(TM) Processor 6276 (64 core) with 250GB Ram.
	\item The multiple cores are not used by the the implementation since no parallelism is implemented yet.
	\item But: Could make use of the available memory now
	\item The java virtual machine was given 64GB, also switched to a different garbage collection algorithm because
	\item Every step in the program is also dumped to harddisk now and loaded when the java virtual machine crashed due to memory outage or Garbage Collection issues.
	\item Still computation time extremly large.
\end{itemize} 

\section{Data Preprocessing}
After loading the xml file the following preprocessing steps have been performed (shortly explain every step with 1 or 2 sentences)
\begin{itemize}
	\item condenseHTMLGUIModel sequences
	\item condenseMouseClicks sequences
	\item correctKeyInteractionTargets sequences
	\item correctTabKeyNavigationOrder sequences
\end{itemize}

\section{Generated Task Trees}
\begin{itemize}
	\item Show some meaningful generated task trees
	\item Show also tasktrees that are not useful
\end{itemize}
\section{Performance Evaluation}

\begin{itemize}
	\item Alot of tables (which step of the algorithm takes how long, for each dataset

	\item Small DataSet Time: real    35m25.965s, user    608m25.525s, sys     26m54.396s
	\item Small DataSet Memory: Arround 25GB
	\item Memory Consummption of data structures i use


\end{itemize}

